Draft information

### 2019-05-15 paper/draft-info.Rmd
Update manuscript changes

## Requests to coauthors

* Specify grant numbers in the Acknowledgements and make sure the ones stated there now are correct. 
* Suggestions to bring the abstract down to 150 words.
* Approve (or not) for submission.

@@

* Fixed typos and minor wording mistakes

>>>>

@@

* Shortened abstract to required length
* Updated grant numbers in acknowledgements 
* References are stored in its own repository (efcaguab/phd-references). Previously, references were accessed by pulling them as a submodule. This created problems when working from different computres. References are now just downloaded from the remote file in the github.
